Simulation Study: Varying Effect Size (t noise)

### 2018-06-06 datasets/simulations/simulations-informative-cubic.Rmd
Add t11 sims for ashq, drop ashq from chisq sim plots

## intermediary files we create below
gauss_file <- file.path(resdir, "informative-cubic-benchmark-gaussian.rds")
tdist_file <- file.path(resdir, "informative-cubic-benchmark-t5.rds")
chisq_file <- file.path(resdir, "informative-cubic-benchmark-chisq4.rds")

@@

# Student's t Setting

@@

@@

```{r chisq4-metrics-covlineplot, results = "hide"}
covariateLinePlot(res, alpha = ualpha, covname = "effect_size")

```{r chisq4-metrics-upset, results = "hide"}
if (numberMethodsReject(resdf, alphacutoff = ualpha, filterSet = excludeSet) >= 3) {
    aggupset(res, alpha = ualpha, supplementary = FALSE, return_list = FALSE)
} else {
    message("Not enough methods found rejections at alpha ", ualpha, 
            "; skipping upset plot")
}
```

>>>>

## intermediary files we create below
gauss_file <- file.path(resdir, "informative-cubic-benchmark-gaussian.rds")
tdist_file <- file.path(resdir, "informative-cubic-benchmark-t5.rds")
tdist11_file <- file.path(resdir, "informative-cubic-benchmark-t11.rds")
chisq_file <- file.path(resdir, "informative-cubic-benchmark-chisq4.rds")

@@

# Student's t Setting (df = 5)

@@

# Student's t Setting (df = 11)

Next, we consider a second setting with t-distributed noise.

```{r t11-parameters}
tstat <- rnorm_generator(6)    # functional: dist of alternative test stats
tstat_dist <- rt_perturber(11)  # functional: sampling dist/noise for test stats
null_dist <- rt_2pvaluer(11)    # functional: dist to calc p-values
seed <- 9158
```

```{r}
bdplust <- modifyBMethod(bdplus, "ashq", df = 11)
```

```{r t11-run-simulation}
if (file.exists(tdist11_file)) {
    res <- readRDS(tdist11_file)
} else {
    res <- mclapply(X = 1:B, FUN = simIteration, bench = bdplust, m = m,
                    pi0 = pi0, tstat = tstat, icovariate = icovariate,
                    tstat_dist = tstat_dist, null_dist = null_dist,
                    seed = seed, mc.cores = cores)
    saveRDS(res, file = tdist11_file)
}
```

```{r t11-one-simulation}
onerun <- simIteration(bdplus, m = m, pi0 = pi0, tstat = tstat, tstat_dist = tstat_dist,
                       icovariate = icovariate, null_dist = null_dist, execute = FALSE)
```

```{r, t11-diag-scatter, results = "hide", fig.width=4.5, fig.height=3.5}
rank_scatter(onerun, pvalue = "pval", covariate = "ind_covariate")
```

```{r, t11-diag-hist, results = "hide", fig.width=10, fig.height=3.2}
strat_hist(onerun, pvalue = "pval", covariate = "ind_covariate", maxy = 5, numQ = 3)
```

```{r t11-metrics-averages, results = "hide"}
resdf <- plotsim_standardize(res, alpha = seq(0.01, 0.10, 0.01))

```{r t11-metrics-covlineplot, results = "hide"}
covariateLinePlot(res, alpha = ualpha, covname = "effect_size")

```{r t11-metrics-upset, results = "hide"}
if (numberMethodsReject(resdf, alphacutoff = ualpha, filterSet = excludeSet) >= 3) {
    aggupset(res, alpha = ualpha, supplementary = FALSE, return_list = FALSE)
} else {
    message("Not enough methods found rejections at alpha ", ualpha, 
            "; skipping upset plot")
}
```

@@

We also take a look at the distribution of rejects for each method as a function of
the effect size and independent covariate. Again, we plot these without `ashq`.

```{r chisq4-metrics-covlineplot, results = "hide"}
covariateLinePlot(lapply(res, function(x) { x[, -which(colnames(x) == "ashq")] }),
                  alpha = ualpha, covname = "effect_size")

covariateLinePlot(lapply(res, function(x) { x[, -which(colnames(x) == "ashq")] }),
                  alpha = ualpha, covname = "ind_covariate")
```

Finally, (if enough methods produce rejections at `r ualpha`) we take a look at
the overlap of rejections between methods. Again, without `ashq`.

```{r chisq4-metrics-upset, results = "hide"}
if (numberMethodsReject(resdf, alphacutoff = ualpha, filterSet = c(excludeSet, "ashq")) >= 3) {
    aggupset(lapply(res, function(x) { x[, -which(colnames(x) == "ashq")] }),
             alpha = ualpha, supplementary = FALSE, return_list = FALSE)
} else {
    message("Not enough methods found rejections at alpha ", ualpha, 
            "; skipping upset plot")
}
```

# Session Info

```{r}
sessionInfo()
```

### 2018-06-06 datasets/simulations/simulations-informative-sine.Rmd
Add t11 sims for ashq, drop ashq from chisq sim plots

## intermediary files we create below
gauss_file <- file.path(resdir, "informative-sine-benchmark-gaussian.rds")
tdist_file <- file.path(resdir, "informative-sine-benchmark-t5.rds")
chisq_file <- file.path(resdir, "informative-sine-benchmark-chisq4.rds")

>>>>

## intermediary files we create below
gauss_file <- file.path(resdir, "informative-sine-benchmark-gaussian.rds")
tdist_file <- file.path(resdir, "informative-sine-benchmark-t5.rds")
tdist11_file <- file.path(resdir, "informative-cubic-benchmark-t11.rds")
chisq_file <- file.path(resdir, "informative-sine-benchmark-chisq4.rds")

### 2018-06-06 datasets/simulations/simulations-informative-step.Rmd
Add t11 sims for ashq, drop ashq from chisq sim plots

## intermediary files we create below
gauss_file <- file.path(resdir, "informative-step-benchmark-gaussian.rds")
tdist_file <- file.path(resdir, "informative-step-benchmark-t5.rds")
chisq_file <- file.path(resdir, "informative-step-benchmark-chisq4.rds")

>>>>

## intermediary files we create below
gauss_file <- file.path(resdir, "informative-step-benchmark-gaussian.rds")
tdist_file <- file.path(resdir, "informative-step-benchmark-t5.rds")
tdist11_file <- file.path(resdir, "informative-step-benchmark-t11.rds")
chisq_file <- file.path(resdir, "informative-step-benchmark-chisq4.rds")

### 2018-06-06 datasets/simulations/simulations-noninformative.Rmd
Add t11 sims for ashq, drop ashq from chisq sim plots

## intermediary files we create below
gauss_file <- file.path(resdir, "noninformative-benchmark-gaussian.rds")
tdist_file <- file.path(resdir, "noninformative-benchmark-t5.rds")
chisq_file <- file.path(resdir, "noninformative-benchmark-chisq4.rds")

>>>>

## intermediary files we create below
gauss_file <- file.path(resdir, "noninformative-benchmark-gaussian.rds")
tdist_file <- file.path(resdir, "noninformative-benchmark-t5.rds")
tdist11_file <- file.path(resdir, "noninformative-benchmark-t11.rds")
chisq_file <- file.path(resdir, "noninformative-benchmark-chisq4.rds")

### 2018-06-06 datasets/simulations/simulations-null.Rmd
Add t11 sims for ashq, drop ashq from chisq sim plots

## intermediary files we create below
gauss_file <- file.path(resdir, "null-benchmark-gaussian.rds")
tdist_file <- file.path(resdir, "null-benchmark-t5.rds")
chisq_file <- file.path(resdir, "null-benchmark-chisq4.rds")

@@

@@

```{r chisq4-metrics-covlineplot, results = "hide"}
covariateLinePlot(res, alpha = 0.05, covname = "effect_size", trans = "log1p")

```{r chisq4-metrics-upset, results = "hide"}
if (numberMethodsReject(resdf, alphacutoff = ualpha, filterSet = excludeSet) >= 3) {
    aggupset(res, alpha = ualpha, supplementary = FALSE, return_list = FALSE) 
} else {
    message("Not enough methods found rejections at alpha ", ualpha, 
            "; skipping upset plot")
}
```

>>>>

## intermediary files we create below
gauss_file <- file.path(resdir, "null-benchmark-gaussian.rds")
tdist_file <- file.path(resdir, "null-benchmark-t5.rds")
tdist11_file <- file.path(resdir, "null-benchmark-t11.rds")
chisq_file <- file.path(resdir, "null-benchmark-chisq4.rds")

@@

# Student's t Setting (df = 11)

```{r t11-parameters}
tstat_dist <- rt_perturber(11)  # functional: sampling dist/noise for test stats
null_dist <- rt_2pvaluer(11)    # functional: dist to calc p-values
seed <- 9158
```

```{r}
bdplust <- modifyBMethod(bdplus, "ashq", df = 11)
```

```{r t11-run-simulation}
if (file.exists(tdist_file)) {
    res <- readRDS(tdist_file)
} else {
    res <- mclapply(X = 1:B, FUN = simIteration, bench = bdplust, m = m,
                    pi0 = pi0, tstat = tstat, icovariate = icovariate,
                    tstat_dist = tstat_dist, null_dist = null_dist,
                    seed = seed, mc.cores = cores)
    saveRDS(res, file = tdist_file)
}
```

```{r t11-one-simulation}
onerun <- simIteration(bdplus, m = m, pi0 = pi0, tstat = tstat, tstat_dist = tstat_dist,
                       icovariate = icovariate, null_dist = null_dist, execute = FALSE)
```

```{r, t11-diag-scatter, results = "hide", fig.width=4.5, fig.height=3.5}
rank_scatter(onerun, pvalue = "pval", covariate = "ind_covariate")
```

```{r, t11-diag-hist, results = "hide", fig.width=10, fig.height=3.2}
strat_hist(onerun, pvalue = "pval", covariate = "ind_covariate", maxy = 5, numQ = 3)
```

```{r t11-metrics-averages, results = "hide"}
resdf <- plotsim_standardize(res, alpha = seq(0.01, 0.10, 0.01))

```{r t11-metrics-covlineplot, results = "hide"}
covariateLinePlot(res, alpha = 0.05, covname = "effect_size", trans = "log1p")

```{r t11-metrics-upset, results = "hide"}
if (numberMethodsReject(resdf, alphacutoff = ualpha, filterSet = excludeSet) >= 3) {
    aggupset(res, alpha = ualpha, supplementary = FALSE, return_list = FALSE) 
} else {
    message("Not enough methods found rejections at alpha ", ualpha, 
            "; skipping upset plot")
}
```

@@

We also take a look at the distribution of rejects for each method as a function of
the effect size and independent covariate. Again, we plot these without `ashq`.

```{r chisq4-metrics-covlineplot, results = "hide"}
covariateLinePlot(lapply(res, function(x) { x[, -which(colnames(x) == "ashq")] }),
                  alpha = ualpha, covname = "effect_size")

covariateLinePlot(lapply(res, function(x) { x[, -which(colnames(x) == "ashq")] }),
                  alpha = ualpha, covname = "ind_covariate")
```

Finally, (if enough methods produce rejections at `r ualpha`) we take a look at
the overlap of rejections between methods. Again, without `ashq`.

```{r chisq4-metrics-upset, results = "hide"}
if (numberMethodsReject(resdf, alphacutoff = ualpha, filterSet = c(excludeSet, "ashq")) >= 3) {
    aggupset(lapply(res, function(x) { x[, -which(colnames(x) == "ashq")] }),
             alpha = ualpha, supplementary = FALSE, return_list = FALSE)
} else {
    message("Not enough methods found rejections at alpha ", ualpha, 
            "; skipping upset plot")
}
```

### 2018-06-06 datasets/simulations/simulations-varyingeffectsize-t.Rmd
Add t11 sims for ashq, drop ashq from chisq sim plots

@@

```{r parameters-shared}
m <- 20000                          # integer: number of hypothesis tests
pi0 <- pi0_sine(0.90)               # numeric: proportion of null hypotheses
tstat_dist <- rt_perturber(5)       # functional: sampling dist/noise for test stats
null_dist <- rt_2pvaluer(5)         # functional: dist to calc p-values
icovariate <- runif                 # functional: independent covariate
```

>>>>

Since all simulation settings in this case study use t-distributed noise, we must specify
the number of degrees of freedom for ASH. We add an additional parameter to the `ashq`
method with the corresponding degrees of freedom of the noise distribution.

```{r}
bdplus <- modifyBMethod(bdplus, "ashq", df = 11)
```

@@

```{r parameters-shared}
m <- 20000                          # integer: number of hypothesis tests
pi0 <- pi0_sine(0.90)               # numeric: proportion of null hypotheses
tstat_dist <- rt_perturber(11)       # functional: sampling dist/noise for test stats
null_dist <- rt_2pvaluer(11)         # functional: dist to calc p-values
icovariate <- runif                 # functional: independent covariate
```
